From physical principles to ???

### 2016-05-11 2015CompleteDerivation/completeDerivation.tex
Adding a section for purely mathematical demonstrations

\newtheorem{assump}{Assumption}
\renewcommand*{\theassump}{\Roman{assump}}
\newtheorem{prop}{Proposition}[section]

@@

	We claim that $\mathcal{S}$ is endowed with a unique Borel measure $\mu$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu$. Let $U \subseteq V \subseteq \mathcal{S}$ two compact subsets. We have $\Lambda_V (\mathcal{c}) = \int_V \rho_{\mathcal{c}} d \mu_V = \int_U \rho_{\mathcal{c}} d \mu_V + \int_{V\backslash U} \rho_{\mathcal{c}} d \mu_V$. We also have $\Lambda_V (\mathcal{c}) = \Lambda_U (\mathcal{c}) + \Lambda_{V\backslash U} (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U + \int_{V \backslash U} \rho_{\mathcal{c}} d \mu_{\overline{V \backslash U}} $. As the two have to be equal for all $U, V, \rho_{\mathcal{c}}$, we must have $\int_{U} \rho_{\mathcal{c}} d \mu_U = \int_{U} \rho_{\mathcal{c}} d \mu_V$. Therefore $d\mu$ is unique and does not depend on the choice of neighborhood. As $\mathcal{S}$ is locally compact, we can find a cover of compact sets. $\Lambda_{\mathcal{S}}(\mathcal{c})$ will be the sum of contributions of the elements of the cover and their intersections. As $\Lambda_U$ is always finite, $\Lambda_{\mathcal{S}}$ is a finite sum of finite contributions. Therefore we have  $\Lambda_{\mathcal{S}} (\mathcal{c}) = \int_{\mathcal{S}} \rho_{\mathcal{c}} d \mu$. The measure is unique on the whole space.

@@

@@

@@

\section{Kinematic equivalence}

@@

>>>>

\newtheorem{assump}{Assumption}
\renewcommand*{\theassump}{\Roman{assump}}
\newtheorem{prop}{Proposition}[section]
\newtheorem{thrm}{Theorem}[section]

@@

	We claim that $\mathcal{S}$ is endowed with a unique Borel measure $\mu$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu$. Let $U \subseteq V \subseteq \mathcal{S}$ two compact subsets. We have $\Lambda_V (\mathcal{c}) = \int_V \rho_{\mathcal{c}} d \mu_V = \int_U \rho_{\mathcal{c}} d \mu_V + \int_{V\backslash U} \rho_{\mathcal{c}} d \mu_V$. We also have $\Lambda_V (\mathcal{c}) = \Lambda_U (\mathcal{c}) + \Lambda_{V\backslash U} (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U + \int_{V \backslash U} \rho_{\mathcal{c}} d \mu_{\overline{V \backslash U}} $. As the two have to be equal for all $U, V, \rho_{\mathcal{c}}$, we must have $\int_{U} \rho_{\mathcal{c}} d \mu_U = \int_{U} \rho_{\mathcal{c}} d \mu_V$. Therefore $d\mu$ is unique and does not depend on the choice of neighborhood. Let $\{U_\alpha\}_{\alpha \in A}$ a cover of $\mathcal{S}$ where each $U_\alpha$ is compact. This is possible as $\mathcal{S}$ is locally compact. We have
\begin{align*}
	\Lambda_{\mathcal{S}}(\mathcal{c}) &= \sum \limits_{\alpha \in A} \Lambda_{U_\alpha}(\mathcal{c}) - \sum \limits_{\alpha \in A} \sum \limits_{\beta \in A}^{\beta \neq\alpha} \Lambda_{U_\alpha \cap U_\beta}(\mathcal{c}) \\
	&= \sum \limits_{\alpha \in A} \int_{U_\alpha} \rho_{\mathcal{c}} d\mu - \sum \limits_{\alpha \in A} \sum \limits_{\beta \in A}^{\beta \neq\alpha} \int_{U_\alpha \cap U_\beta}(\mathcal{c}) \rho_{\mathcal{c}} d\mu \\
	 &= \int_{\mathcal{S}} \rho_{\mathcal{c}} d\mu
\end{align*}
	as $\Lambda_U$ is always finite. The measure is unique on the whole space.

@@

As we identified $C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ as the set of distributions that are physically meaningful, it's useful to show how commonly used functions spaces do not fit the bill. We do this briefly by finding counterexample. The set of continuous functions $C(\mathcal{S})$ would include functions that diverge at infinity. The set of continuous functions with compact support $C_C(\mathcal{S})$ would exclude Gaussians. The set of continuous functions that vanish at infinity $C_0(\mathcal{S})$ includes function whose integral is infinite. Schwartz space $S(\mathcal{S})$ requires functions to be infinitely smooth and we do not see a physical requirement for that.

@@

TODO

@@

\section{Kinematic equivalence}
TODO

@@

\section{Appendix: mathematical support}

In this section we include mathematical demonstration in support of the physical arguments of the paper.

\begin{thrm}\label{everywhere_integrable_is_lebesgue_integrable}
	Let $\mathcal{L}(S,\mu) \equiv \{ \rho : S \rightarrow \mathbbm{R} \; | \;\; |\int_{U} \rho d\mu| < \infty \; \forall U \subseteq S\}$. $\mathcal{L}(S,\mu)=L^1(S,\mu)$ where $L^1(S,\mu) = \{ \rho : S \rightarrow \mathbbm{R} \; | \;\; \int_{S} |\rho| d\mu < \infty \}$
\end{thrm}

\begin{proof}
	We claim $\mathcal{L}(S,\mu) \supseteq L^1(S,\mu)$. Let $\rho \in L^1(S,\mu)$. Let $U \subseteq S$. $\lVert \rho \rVert_U \equiv \int_{U} |\rho| d\mu < \int_{\mathcal{S}} |\rho| d\mu < \infty$. $\lVert \rho \rVert_U = \lVert \rho^+ \rVert_U + \lVert \rho^- \rVert_U$. $\lVert \rho^+ \rVert_U < \infty$ and $\lVert \rho^- \rVert_U < \infty$. $|\int_{U} \rho d\mu| = |\int_{U} \rho^+ d\mu - \int_{U} \rho^- d\mu| = |\int_{U} \rho^+ d\mu| - |\int_{U} \rho^- d\mu| = \lVert \rho^+ \rVert_U - \lVert \rho^- \rVert_U < \infty$. $\rho \in\mathcal{L}(S,\mu)$.

	We claim $L^1(S,\mu) \supseteq \mathcal{L}(S,\mu)$.  Let $\rho \in \mathcal{L}(S,\mu)$. Let $S^+ \equiv  \{ s \in S \; | \; \rho(s) > 0\}$. Let $S^- \equiv  \{ s \in S \; | \; \rho(s) < 0\}$. $|\int_{S^+} \rho d\mu| = |\int_{S} \rho^+ d\mu| = \lVert \rho^+ \rVert < \infty$ and $|\int_{S^-} \rho d\mu| = |\int_{S} \rho^- d\mu| = \lVert \rho^- \rVert < \infty$. $\lVert \rho \rVert = \lVert \rho^+ \rVert_U + \lVert \rho^- \rVert_U < \infty$. $\rho \in L^1(S,\mu)$.

	We claim $L^1(S,\mu) = \mathcal{L}(S,\mu)$. $\mathcal{L}(S,\mu) \supseteq L^1(S,\mu)$ and $L^1(S,\mu) \supseteq \mathcal{L}(S,\mu)$.	
\end{proof}

\begin{thrm}[Modified Riesz theorem]\label{modified_riesz_theorem}
	Let $\mathcal{L}(S,\mu) \equiv \{ \rho : S \rightarrow \mathbbm{R} \; | \;\; |\int_{U} \rho d\mu| < \infty \; \forall U \subseteq S\}$. $\mathcal{L}(S,\mu)=L^1(S,\mu)$ where $L^1(S,\mu) = \{ \rho : S \rightarrow \mathbbm{R} \; | \;\; \int_{S} |\rho| d\mu < \infty \}$
\end{thrm}
